MS Depression Paper, post replication, started 2022 09 21

### 2023-03-09 scripts/msdepression_n380_started_20230113_post_replication_just_simple_mm.Rmd
Add files via upload
Formatted (Left) (Right)

>>>>

#create data frame with fascicles sorted by overlap with depression network, replace abbreviations with full fascicle names and swap _ for space in the full name
df_fascicles_sorted_by_volume_in_mask <- fascicle_volumes_dep_network_no_cranial_nerves %>%  
  replace(is.na(.), 0) %>% 
  arrange(desc(non_zero_voxels_in_dep_map)) %>% 
  left_join(full_fascicle_names, by = c("fascicle" = "Abbreviation")) %>%
  mutate(full_fascicle_name_space = str_replace_all(Full_name, pattern = "_", replacement = " ")) %>%
  mutate(full_fascicle_name_space = str_replace(full_fascicle_name_space, pattern = " R$", replacement = " (Right)")) %>%
  mutate(full_fascicle_name_space = str_replace(full_fascicle_name_space, pattern = " L$", replacement = " (Left)")) %>%
  mutate(full_fascicle_name_space = gsub(pattern = "([0-9])", replacement = " \\1", x = full_fascicle_name_space))

write.table(df_fascicles_sorted_by_volume_in_mask, paste0(homedir, "/results/df_fascicles_sorted_by_volume_in_mask_for_eTable3.csv"), quote = F, sep = ",") #had to manually change the spreadsheet because the dictionary is based on a spelling mistake - C_R_R is Cingulum Rarolfactory in the dictionary, but should be Parolfactory
